SubsidyExplorer - Step 3: Model Parameterization

### 2020-04-24 scripts/04_model_parameterization.Rmd
gfw analysis updated

# Directories for the output files generated by this script
results_dir <- here::here("results", "3-model-parameterization/")
if (dir.exists(results_dir) == F) {
  dir.create(results_dir, recursive = T)
}

@@

# Define regions 
region_names <- sort(c("atlantic", "indian", "pacific_e", "pacific_w"))

# Create a tidy df with the cooresponding fao regions
regions_tidy <- tibble(
  region = region_names,
  fao_region = list(c(21, 27, 37, 31, 34, 41, 47, 18, 48), c(51, 57, 58), c(67, 77, 87), c(61, 71, 81, 88))
) %>%
  unnest(cols = c(fao_region))

@@

```{r}
# Load data sets
# Load costello data
costello_2016_dat <- read_csv(costello_2016_path) %>%
  clean_names(case = "snake")

@@

# Create cutoffs determining which vessels are in which fleets
managed_cutoff <- quantile(vessel_list_mgmt$fmi_best, probs = seq(0,1,0.33))[3]

# Assign management criteria
vessel_list_out <- vessel_list_mgmt %>%
  mutate(fleet = case_when(fmi_best >= managed_cutoff ~ "managed",
                           TRUE ~ "open_access")) %>%
  left_join(regions_tidy, by = c("fao_region" = "fao_region"))

@@

For our biomass growth function, $G(b)$, we use a form of the basic logistic surplus production model commonly referred to as the Pella-Tomlinson Model. With discrete units of time (hereafter years for the purposes of our model), biomass in the next year, $b_{t+1}$, is given by:

$$ b_{t+1} = b_{t} + \frac{\phi + 1}{\phi} r b_{t}\Bigg(1 - \bigg(\frac{b_{t}}{K}\bigg)^{\phi}\Bigg) - h_{t}$$
where $\phi$ is the Pella-Tomlinson parameter that allows for asymmetry in the production curve (centered on $phi = 1$), $r$ characterizes the intrinsic growth rate of the global stock, $K$ is the carrying capacity (maximum population size for growth to be positive), and $h_t$ is the total harvest in that year across all fleets.

Certain attributes of the Pella-Tomlinson biomass growth function relate its paramters to stock characteristics. For instance, $r$ can be calculated as

$$ r = \bigg(\frac{MSY}{K} \bigg) (\phi + 1)^{\frac{1}{\phi}} $$

where $MSY$ is the maximum sustinable yield of the stock, and $K$ is the carrying capacity of the stock.

We therefore need to estimate the following parameters for the biomass growth function: 
- $\phi$ : Pella-Tomlinson shape parameter (no units)
- $MSY$ : Global maximum sustainable yield (tons)
- $K$ : Global biomass carrying capacity (tons)
- $r$ : Global biomass intrinsic growth rate (no units)

The following parameters will be estimated prior to each model run:
- $b_0$ : Global biomass in the base year (tons)

<!-- ## Alternative form of the Pella-Tomlinson biomass growth function -->

<!-- The biomass growth function can also be written as: -->

<!-- $$ G(b) = \alpha b - \beta b^\phi $$ -->
<!-- where $\phi$ is the Pella-Tomlinson exponent dictating how skewed the growth curve is (centered on $\phi = 2$), $\alpha$ is the intrinsic growth rate, and $\beta$ is another parameter.  -->

<!-- In this case, $\alpha$ can be estimated as: -->

<!-- $$ \alpha = \bigg(\frac{MSY}{K}\bigg) \bigg(\frac{\phi^\frac{\phi}{\phi - 1}}{\phi - 1}\bigg) $$ -->

<!-- where $MSY$ is the maximum sustinable yield of the stock, and $K$ is the carrying capacity of the stock.  -->

<!-- Similarly, $\beta$ can be estimated as:  -->

<!-- $$ \beta = \bigg(\frac{MSY}{K^\phi}\bigg) \bigg(\frac{\phi^\frac{\phi}{\phi - 1}}{\phi - 1}\bigg) $$ -->

@@

Very little is known about the global carrying capacity of fish stocks, though many studies have suggested that it is between 5 and 15 times the MSY for different species of fish. Again using the database of stock statuses created by Costello et al. (2016), we can obtain an estimate of global carrying capacity by summing the carrying capacities of all stocks contained in this dataset, adjusted for the fraction of global biomass estimated to be represented by this data.

```{r}
# One estimate of global carrying capacity
global_k <- sum(costello_2016_dat$k)/0.78
```

That yields a global carrying capacity equal to `r format(global_k, big.mark = ",")` tons, which is `r global_k/global_msy` times our estimate of global MSY. We not that this is  significantly higher than estimates of global carrying capacity used by other studies.

```{r}
# Add K to parameter table
global_model_parameters <- global_model_parameters %>%
  bind_rows(tibble(parameter = "K", value = global_k, source = "Costello et al. 2016"))
```

<!-- That yields a global carrying capacity equal to `r format(global_k, big.mark = ",")` tons, which is much closer to the estimate of 980 million tons used by the World Bank (2017) study.  -->

We can then use all three parameters to estimate the global intrinsic growth rate.

@@

```{r}
# # NEED TO FIX THIS
global_biomass <- global_k*0.306

# Add base year biomass to parameter table
# global_model_parameters <- global_model_parameters %>%
#   bind_rows(tibble(parameter = "B0", value = global_biomass, source = "Costello et al. 2016"))
```

@@

We also apply our bio-economic model of fisheries subsidies reform on a regional basis. For this analysis, we have chosen to use five regions based loosly on the major ocean basins and using the FAO statistical regions as subdivisions as needed to further separate regions: Arctic (18), Atlantic and Mediterranean (21, 27, 31, 34, 37, 41, 47), Indian (51, 57), Eastern Pacific (67, 77, 87), Western Pacific (61, 71, 81), and Southern (48, 58, 88).

@@

```{r}
# Create new row for every FAO statistical region - For stocks spanning multiple fao statistical regions, we assume msy/carrying capacity is split equally between them. 
# In most cases this doesn't matter since we've defined our regions in a way where the entire stock is in the same region, even if it spans multiple fao statistical areas 
costello_2016_dat_edit <- costello_2016_dat %>%
  mutate(region_fao_chr = as.character(region_fao),
         n_regions = nchar(region_fao_chr)/2,
         region_fao_split = str_split(gsub("(.{2})", "\\1 ", region_fao_chr), " ")) %>%
  unnest(cols = c(region_fao_split)) %>%
  mutate(region_fao_split = as.numeric(region_fao_split)) %>%
  dplyr::filter(region_fao_split != "") %>%
  mutate(msy_new = msy/n_regions,
         k_new = k/n_regions,
         biomass_new = biomass/n_regions,
         catch_new = catch/n_regions) %>%
  left_join(regions_tidy, by = c("region_fao_split" = "fao_region"))

# Now aggregate by region
costello_regional_dat <- costello_2016_dat_edit %>%
  group_by(region) %>%
  summarize(msy = sum(msy_new, na.rm = T)/0.78,
            k = sum(k_new, na.rm = T)/0.78,
            price = median(price, na.rm = T),
            bv_bmsy = median(bv_bmsy, na.rm = T),
            biomass = sum(biomass_new, na.rm = T),
            catch = sum(catch_new, na.rm = T)) %>%
  arrange(region)

# Extract msy
regional_msy <- round(costello_regional_dat$msy)
names(regional_msy) <- region_names

@@

We do the same for regional carrying capacities.

```{r}
# Extract carrying capacity
regional_k <- round(costello_regional_dat$k)
names(regional_k) <- region_names

# Add MSY to the regional paramter table
regional_model_parameters <- regional_model_parameters %>%
  bind_rows(c("parameter" = "K", "source" = "Costello et al. 2016", regional_k))
```

@@

```{r}
# # NEED TO FIX THIS
regional_biomass <- regional_k * 0.306

# Add biomass to parameter table
# regional_model_parameters <- regional_model_parameters %>%
#   bind_rows(c("parameter" = "B0", "source" = "Costello et al. 2016", regional_biomass))
```

@@

<!-- ## Global harvest parameters -->

<!-- We calculate base year harvest for each fleet based on total marine capture production (2017) from the FAO.  -->

```{r}
# Group by fleet and calculate base year harvest and effort for the global fleet
global_fleet <- vessel_list_out %>%
  group_by(fleet) %>%
  summarize(vessels = n_distinct(ssvid),
            fishing_KWh = sum(fishing_KWh_eez_fao, na.rm = T),
            catch = sum(catch, na.rm = T),
            revenue = sum(revenue, na.rm = T),
            bad_subs = sum(bad_subs, na.rm = T))

# Add base year harvest to parameter table
# global_model_parameters <- global_model_parameters %>%
#   bind_rows(tibble(parameter = "h0_managed", value = global_fleet$catch[global_fleet$fleet == "managed"], source = "FAO 2019"))
# global_model_parameters <- global_model_parameters %>%
#   bind_rows(tibble(parameter = "h0_oa", value = global_fleet$catch[global_fleet$fleet == "open_access"], source = "FAO 2019"))

Base gear effort for each fleet comes from GFW data (2018). Effort is given in units of kW hours, which is a combination of the hours spent engaged in fishing activity, and the engine capacity of the vessel in KW.

```{r}
# global_model_parameters <- global_model_parameters %>%
#   bind_rows(tibble(parameter = "e0_managed", value = global_fleet$fishing_KWh[global_fleet$fleet == "managed"], source = "GFW 2019"))
# global_model_parameters <- global_model_parameters %>%
#   bind_rows(tibble(parameter = "e0_oa", value = global_fleet$fishing_KWh[global_fleet$fleet == "open_access"], source = "GFW 2019"))
```

We then estimate catchability for both fleets using the equation listed above

```{r}
catchability_global <- global_fleet$catch/(global_biomass*global_fleet$fishing_KWh)

# global_model_parameters <- global_model_parameters %>%
#   bind_rows(tibble(parameter = "q_managed", value = catchability_global[1], source = "FAO 2019; GFW 2019"))
# global_model_parameters <- global_model_parameters %>%
#   bind_rows(tibble(parameter = "q_oa", value = catchability_global[2], source = "FAO 2019; GFW 2019"))
```

@@

We do the same process to calculate base year harvest and effort, but aggregate by fleet and region.

```{r}
# Assign regions
# vessel_list_out <- vessel_list_out %>%
#   left_join(regions_tidy, by = c("fao_region" = "fao_regions"))

# Group by fleet and calculate base year harvest and effort for the global fleet
regional_fleet <- vessel_list_out %>%
  group_by(region, fleet) %>%
  summarize(vessels = n_distinct(ssvid),
            fishing_KWh = sum(fishing_KWh_eez_fao, na.rm = T),
            catch = sum(catch, na.rm = T),
            revenue = sum(revenue, na.rm = T),
            bad_subs = sum(bad_subs, na.rm = T)) %>%
  arrange(region, fleet)

# Get harvest
regional_fleet_harvest <- regional_fleet %>%
  dplyr::select(region, fleet, catch) %>%
  spread(region, catch)

# Get effort
regional_fleet_effort <- regional_fleet %>%
  dplyr::select(region, fleet, fishing_KWh) %>%
  spread(region, fishing_KWh)

# Add base year harvest to parameter table
# regional_model_parameters <- regional_model_parameters %>%
#   bind_rows(c("parameter" = "h0_managed", "source" = "FAO 2019", unlist(regional_fleet_harvest[1,-1])))
# regional_model_parameters <- regional_model_parameters %>%
#   bind_rows(c("parameter" = "h0_oa", "source" = "FAO 2019", unlist(regional_fleet_harvest[2,-1])))
# 
# # Add base year effort to parameter table
# regional_model_parameters <- regional_model_parameters %>%
#   bind_rows(c("parameter" = "e0_managed", "source" = "GFW 2019", unlist(regional_fleet_effort[1,-1])))
# regional_model_parameters <- regional_model_parameters %>%
#   bind_rows(c("parameter" = "e0_oa", "source" = "GFW 2019", unlist(regional_fleet_effort[2,-1])))
```

Now we calculate catchability for each fleet regionally

```{r}
# Calculate catchability regionally
catchability_regional <- tibble(fleet = c("managed", "open_access"))

for(i in 2:ncol(regional_fleet_harvest)){

  out <- tibble(unlist(regional_fleet_harvest[,i])/(regional_biomass[i-1]*unlist(regional_fleet_effort[,i])))
  colnames(out) <- region_names[i-1]

  catchability_regional <- catchability_regional %>%
    bind_cols(out)

}
# Add catchability to parameter table
# regional_model_parameters <- regional_model_parameters %>%
#   bind_rows(c("parameter" = "q_managed", "source" = "FAO 2019; GFW 2019", unlist(catchability_regional[1,-1])))
# regional_model_parameters <- regional_model_parameters %>%
#   bind_rows(c("parameter" = "q_oa", "source" = "FAO 2019; GFW 2019", unlist(catchability_regional[2,-1])))

@@

where $\epsilon$ is the constant elasticity of demand, and $\delta$ is a constant. We calculate the parameter $\delta$ using data from Costello et al. (2016) as follows:

$$ \delta = \frac{h_{2012}}{(p_{2012})^{\epsilon}}$$

We therefore need to estimate the following parameters for the demand function: 
- $\epsilon$ : price flexibility/constant elasticity of demand

The following parameters are calculated prior to each time step: 
- $\delta$ : price constant

>>>>

# Directories for the output files generated by this script
results_dir <- here::here("results", "04-model-parameterization/")
if (dir.exists(results_dir) == F) {
  dir.create(results_dir, recursive = T)
}

@@

# Define regions 
region_names <- sort(c("atlantic_e", "atlantic_w", "indian", "pacific_e", "pacific_w", "polar"))

# Create a tidy df with the cooresponding fao regions
regions_tidy <- tibble(
  region = region_names,
  fao_region = list(c(27, 37, 34, 47), # atlantic east + med
                    c(21, 31, 41), # atlantic west
                    c(51, 57), # indian
                    c(67, 77, 87), # pacific e
                    c(61, 71, 81),# pacific w 
                    c(18, 48, 58, 88)) # polar
) %>%
  unnest(cols = c(fao_region))

@@

```{r}
# Load data sets
# Load costello data
costello_2016_dat <- read_csv(costello_2016_upsides_dat_path)

@@

# Assign regions to vessels
vessel_list_out <- vessel_list_mgmt %>%
  left_join(regions_tidy, by = c("fao_region" = "fao_region"))

# Save updated vessel list
write_csv(vessel_list_out, paste0(results_dir, "vessel_list_2018_regions.csv"))
```

@@

For our biomass growth function, $G(b)$, we use a form of the basic logistic surplus production model commonly referred to as the Pella-Tomlinson model. With discrete units of time (hereafter years for the purposes of our model), biomass in the next year, $b_{t+1}$, is described by:

$$ b_{t+1} = b_{t} + \frac{\phi + 1}{\phi} g b_{t}\Bigg(1 - \bigg(\frac{b_{t}}{K}\bigg)^{\phi}\Bigg) - h_{t}$$
where $\phi$ is a scaling parameter, $g$ is the population growth rate, $K$ is the carrying capacity (maximum population size for growth to be positive), and $h_t$ is the total harvest in that year across all fleets.

The intrinsic growth rate of the global stock ($r$) is given by: 
$$r = \frac{\phi + 1}{\phi}g$$

Certain attributes of the Pella-Tomlinson biomass growth function relate its parameters to stock characteristics. For instance, $g$ is equal to

$$ g = \bigg(\frac{MSY}{K} \bigg) (\phi + 1)^{\frac{1}{\phi}} $$
where $MSY$ is the maximum sustinable yield of the stock, and $K$ is the carrying capacity of the stock.

Maximum sustainable yield is therefore equal to: 
$$MSY = \frac{gK}{(\phi + 1)^{\frac{1}{\phi}}} $$
and the biomass cooresponding to MSY as: 
$$B_{MSY} = \frac{K}{(\phi + 1)^{\frac{1}{\phi}}}$$

$B_{MSY}/K$ is given by: 
$$\frac{B_{MSY}}{K} = \frac{1}{(\phi + 1)^{\frac{1}{\phi}}}$$
where a value of $\phi = 1$ makes this equation equal to the Schaefer model (production function is symmetrical).

We therefore need to assign the following parameters for the biomass growth function: 
- $\phi$ : Scaler parameter (no units)
- $MSY$ : Global maximum sustainable yield (tons)
- $K$ : Global biomass carrying capacity (tons)
- $r$ : Global biomass population growth rate (no units)
- $h_0$: Total harvest in the base year (tons)
- $b_0$ : Global biomass in the base year (tons)

### Alternate forms of the Pella-Tomlinson model

### Discrete

The Sunken Billions reports also used a form of the Pella-Tomlinson model, though they defined it differently. The form of the model used there may be written as:

$$ G(X) = r X - \beta X^{\gamma} $$
where $X$ is biomass, $\gamma$ is the Pella-Tomlinson exponent that defines the skewness of the biomass growth function, $r$ is the intrinsic growth rate, and $\beta$ is a parameter.

In this form, values of $\gamma < 2$ skew the function to the left, values of $\gamma > 2$ skew the function to the right, and $\gamma = 2$ reproduces the Lotka-Volterra logistic function (Schaefer) model (symmetric). As $\gamma$ gets closer to 1, it converges on the Fox biomass growth function.

$X_{MSY}/K \in [0.368,1]$ for $\gamma$ values ranging from unity to infinity. In general, there are biological reasons to expect this to occur at a value less than 0.5 cooreponding to a $\gamma < 2$. This ratio can be caclulated as:

$$\frac{X_{MSY}}{K} = \gamma^{\frac{1}{1-\gamma}}$$

With this form of the model, carrying capacity ($K$) is given by:
$$K = \bigg(\frac{r}{\beta}\bigg)^{\frac{1}{\gamma-1}} $$
Maximum sustainable yield can then be calculated as:
$$ MSY = r \bigg(\frac{\gamma-1}{\gamma}\bigg)\bigg(\frac{r}{\gamma\beta}\bigg)^{\frac{1}{\gamma-1}} $$
and the biomass cooresponding to MSY as: 
$$ X_{MSY} = \bigg(\frac{r}{\gamma\beta}\bigg)^{\frac{1}{\gamma-1}}$$

@@

Very little is known about the global carrying capacity of fish stocks, though many studies have suggested that it is between 5 and 15 times the MSY for different species of fish. The estimate of global carrying capacity obtained by summing the respective carrying capacities all all stocks from Costello et al. (2016) is higher than this (22 times MSY). We therefore instead assume global carrying capacity to be equal to 9.1 times MSY as found in the second Sunken Billions report.

```{r}
# One estimate of global carrying capacity
# global_k <- sum(costello_2016_dat$k)/0.78
global_k <- global_msy*9.6

# Add K to parameter table
global_model_parameters <- global_model_parameters %>%
  bind_rows(tibble(parameter = "K", value = global_k, source = "Costello et al. 2016; World Bank 2017"))
```

We can then use all three parameters to estimate the global biomass intrinsic growth rate using the equation above.

@@

A great deal of uncertainty exists about the total amount of biomass currently in our oceans. We therefore estimate total biomass in the base year (2018) by assuming an annual rate of biomass growth of 8 million mt/year (World Bank 2017). We then solve for the biomass in 2018 that would have yielded the observed harvest after accounting for the assummed rate of biomass growth ($\xi = 8000000$)  $b_{t+1} = b_t + \xi$

$$ h_0+ \xi =\frac{\phi + 1}{\phi} r b_{0}\Bigg(1 - \bigg(\frac{b_{0}}{K}\bigg)^{\phi}\Bigg)$$

```{r}
# Calculate global total harvest
global_h0 <- sum(vessel_list_out$catch, na.rm = T)

# Add base year harvest to parameter table
global_model_parameters <- global_model_parameters %>%
  bind_rows(tibble(parameter = "h0", value = global_h0, source = "FAO 2019"))
```

```{r}
# Estimation of starting biomass
biomass_vec <- seq(0, 0.5*global_k, length.out = 2000)
growth_approx <- (((phi+1)/phi)*global_r*biomass_vec*(1-((biomass_vec/global_k)^phi)))
biomass_pos <- which.min(abs(growth_approx - (global_h0+8000000)))
global_b0 <- biomass_vec[biomass_pos]

# Add base year biomass to parameter table
global_model_parameters <- global_model_parameters %>%
  bind_rows(tibble(parameter = "B0", value = global_b0, source = "FAO 2019; World Bank 2017"))
```

@@

We also apply our bio-economic model of fisheries subsidies reform on a regional basis. For this analysis, we have chosen to use six regions based loosly on the major ocean basins and using the FAO statistical regions as subdivisions as needed to further separate regions: Atlantic Ocean (East) and Mediterranean [`r paste(regions_tidy$fao_region[regions_tidy$region == "atlantic_e"], collapse = ", ")`], Atlantic Ocean (West) [`r paste(regions_tidy$fao_region[regions_tidy$region == "atlantic_w"], collapse = ", ")`], Indian Ocean [`r paste(regions_tidy$fao_region[regions_tidy$region == "indian"], collapse = ", ")`], Pacific Ocean (East) [`r paste(regions_tidy$fao_region[regions_tidy$region == "pacific_e"], collapse = ", ")`], Pacific Ocean (West) [`r paste(regions_tidy$fao_region[regions_tidy$region == "pacific_w"], collapse = ", ")`], and Polar Oceans [`r paste(regions_tidy$fao_region[regions_tidy$region == "polar"], collapse = ", ")`].

@@

```{r}
# Calculate stats by region
costello_2016_dat_regional <- costello_2016_dat %>%
  dplyr::filter(region_fao_split != "") %>%
  mutate(msy_new = (msy/0.78)/n_regions) %>%
  left_join(regions_tidy, by = c("region_fao_split" = "fao_region")) %>%
  group_by(region) %>%
  summarize(msy = sum(msy_new, na.rm = T),
            price = median(price, na.rm = T)) %>%
  arrange(region)

# Extract msy
regional_msy <- round(costello_2016_dat_regional$msy)
names(regional_msy) <- region_names

@@

We estimate regional carrying capacities again by assuming K to be 9.6 times MSY.

```{r}
# Extract carrying capacity
regional_k <- regional_msy*9.6

# Add MSY to the regional paramter table
regional_model_parameters <- regional_model_parameters %>%
  bind_rows(c("parameter" = "K", "source" = "Costello et al. 2016; World Bank 2017", regional_k))
```

@@

```{r}
# Calculate global total harvest
regional_h0 <- (vessel_list_out %>%
  group_by(region) %>%
  summarize(catch = round(sum(catch, na.rm = T))))$catch
names(regional_h0) <- region_names

# Add base year harvest to parameter table
regional_model_parameters <- regional_model_parameters %>%
  bind_rows(c("parameter" = "h0", "source" = "FAO 2019", regional_h0))
```

```{r}
#Estimate starting biomass
regional_b0 <- numeric(length(region_names))
regional_biomass_growth <- c(4.1e6, 8e6, -2e6, 2.3e6, 2.3e6, -2e6)

for(i in 1:length(regional_h0)){
  biomass_vec <- seq(0, regional_k[i], length.out = 10000)
  growth_approx <- (((regional_phi[i]+1)/regional_phi[i])*regional_r[i]*biomass_vec*(1-((biomass_vec/regional_k[i])^regional_phi[i])))
  biomass_pos <- which.min(abs(growth_approx - (regional_h0 + regional_biomass_growth[i])))
  regional_b0[i] <- biomass_vec[biomass_pos] 
}
names(regional_b0) <- region_names

# Add base year biomass to parameter table
regional_model_parameters <- regional_model_parameters %>%
  bind_rows(c("parameter" = "b0", "source" = "FAO 2019; World Bank 2017", regional_b0))
```

@@

## Global harvest parameters

Though we don't calculate the fleet specific parameters here, we have already calculated total harvest in the base year, and can calculate total fishing effort. This data comes from GFW data (2018). Effort is given in units of kWh, which is the product of the hours spent engaged in fishing activity, and the engine capacity of the vessel in kW

```{r}
# Group by fleet and calculate base year harvest and effort for the global fleet
global_e0 <- sum(vessel_list_out$fishing_KWh_eez_fao_ter, na.rm = T)

# Add base year effort to parameter table
global_model_parameters <- global_model_parameters %>%
  bind_rows(tibble(parameter = "e0", value = global_e0, source = "GFW 2019"))
```

@@

We do the same process to calculate base year total effort by region

```{r}
# Group by fleet and calculate base year harvest and effort for the global fleet
regional_fleet <- vessel_list_out %>%
  group_by(region) %>%
  summarize(vessels = n_distinct(ssvid),
            fishing_KWh = sum(fishing_KWh_eez_fao_ter, na.rm = T),
            bad_subs = sum(bad_subs, na.rm = T)) %>%
  arrange(region)

# Get effort
regional_e0 <- regional_fleet$fishing_KWh
names(regional_e0) <- region_names

# Add base year effort to parameter table
regional_model_parameters <- regional_model_parameters %>%
  bind_rows(c("parameter" = "e0", "source" = "GFW 2019", regional_e0))
```

@@

where $\epsilon$ is the constant elasticity of demand, and $\delta$ is a constant. We calculate the parameter $\delta$ using data as follows:

$$ \delta = \frac{h_{0}}{(p_{0})^{\epsilon}}$$

We therefore need to estimate the following parameters for the demand function: 
- $\epsilon$ : price flexibility/constant elasticity of demand
- $p_0$: global price in the base year (2018)
